# (APPENDIX) Appendix {-}

# Post template in Markdown {#templatemd}

Use of this template is described in [Start the post from a template](#templates) and [Walkthrough with code snippets](#usetemplates).

Markdown template to be saved as `/content/blog/YYYY-MM-DD-slug/index.md`

You can hover over the top-right corner of the template to make a copy-paste button appear.

```{r posttemplatemd, results="asis"}
show_template("post-template.md", lang = "markdown")
```

# Post template in R Markdown {#templatermd}

Use of this template is described in [Start the post from a template](#templates) and [Walkthrough with code snippets](#usetemplates).

R Markdown template to be saved as `/content/blog/YYYY-MM-DD-slug/index.Rmd`

[Available on GitHub](https://github.com/ropensci-org/blog-guidance/blob/master/templates/post-template.Rmd) (_not displayed for copy-paste because of "html_preserve" tags_)

# Author file template {#authortemplate}

Use of this template is described in [Create or update your author file](#createauthorfile).

Author file template to be saved as `/content/authors/yourfirstname-yourlastname/_index.md` as described in [Technical Guidelines](#createauthorfile).

You can hover over the top-right corner of the template to make a copy-paste button appear.

```{r authorfiletemplate, results="asis"}
show_template("author-file-template.md", lang = "yaml")
```

# Author checklist for a post about a peer-reviewed package {#authorchecklistpeer}

Use of this template is described in [Pre-submission checks](#presubchecks).

Copy this checklist into the first comment on your pull request.
You can hover over the top-right corner of the template to make a copy-paste button appear.

```{r checklistpkg2, echo = FALSE}
show_checklist(c("submission-checklist.csv", "submission-checklist-peer-reviewed-pkg.csv"))
```

# Author checklist for any other post {#authorchecklistany}

Use of this template is described in [Pre-submission checks](#presubchecks).

Copy this checklist into the first comment on your pull request. 
You can hover over the top-right corner of the template to make a copy-paste button appear.

```{r checklistother2, echo = FALSE}
show_checklist("submission-checklist.csv")
```

# Editor checklist for a post about a peer-reviewed package {#editorchecklistpeer}

Use of this template is described in [Review a Post](#review).

Copy this checklist to your GitHub review summary.
You can hover over the top-right corner of the template to make a copy-paste button appear.

```{r checklisteditor2, echo = FALSE}
show_checklist(c("editor-checklist.csv", "editor-checklist-peer-reviewed-pkg.csv"))
```

# Editor checklist for any other post {#editorchecklistany}

Use of this template is described in [Review a Post](#review).

Copy this checklist to your GitHub review summary.
You can hover over the top-right corner of the template to make a copy-paste button appear.

```{r checklisteditorprp2, echo = FALSE}
show_checklist("editor-checklist.csv")
```

# Understanding Twitter cards {#twittercards}

A [Twitter card](https://developer.twitter.com/en/docs/tweets/optimize-with-cards/overview/abouts-cards) means than when a URL is included in a tweet, what other Twitter users see is not the URL but instead a "card", i.e. the metadata from the URL rendered in a nice preview.
The Twitter metadata in a [post's YAML](whatgoesinyaml) helps it "look good" when an account like R Weekly Live or other readers link to the post in a tweet. 
The relevant YAML tags for rOpenSci posts are `title`, `description`, `twitterImg`.
These same metadata tags might be picked up by other platforms such as Slack.

This is what a tweet about an rOpenSci post looks like by default.

<!--html_preserve--><blockquote class="twitter-tweet"><p lang="en" dir="ltr">rOpenSci&#39;s Leadership in <a href="https://twitter.com/hashtag/rstats?src=hash&amp;ref_src=twsrc%5Etfw">#rstats</a> Culture <a href="https://twitter.com/rOpenSci?ref_src=twsrc%5Etfw">@rOpenSci</a> <a href="https://twitter.com/hashtag/rstats?src=hash&amp;ref_src=twsrc%5Etfw">#rstats</a> <a href="https://twitter.com/hashtag/datascience?src=hash&amp;ref_src=twsrc%5Etfw">#datascience</a> <a href="https://t.co/VWSmvstOED">https://t.co/VWSmvstOED</a></p>&mdash; R Weekly Live (@rweekly_live) <a href="https://twitter.com/rweekly_live/status/1230932166306983936?ref_src=twsrc%5Etfw">February 21, 2020</a></blockquote> <script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script> <!--/html_preserve-->

If a specific `description` is not specified, the first sentences of the post (~100 characters) are used.
If a specific `twitterImg` is not specified, a thumbnail of the rOpenSci logo is used. 

This is what a tweet about an rOpenSci post looks like with YAML `twitterImg` specified.

<!--html_preserve--><blockquote class="twitter-tweet"><p lang="en" dir="ltr">Aggregating spatial data with the grainchanger package <a href="https://twitter.com/rOpenSci?ref_src=twsrc%5Etfw">@rOpenSci</a> <a href="https://twitter.com/hashtag/rstats?src=hash&amp;ref_src=twsrc%5Etfw">#rstats</a> <a href="https://twitter.com/hashtag/datascience?src=hash&amp;ref_src=twsrc%5Etfw">#datascience</a> <a href="https://t.co/eILe7af7o8">https://t.co/eILe7af7o8</a></p>&mdash; R Weekly Live (@rweekly_live) <a href="https://twitter.com/rweekly_live/status/1151027589831462912?ref_src=twsrc%5Etfw">July 16, 2019</a></blockquote> <script async src="https://platform.twitter.com/widgets.js" charset="utf-8"></script>  <!--/html_preserve-->

If you specify a `twitterImg`, ensure that its dimensions are appropriate. 
(Google those for current recommendation.) 
These may be different from the dimensions of an image featured in your post. 
You could save a separate copy of an image for the purpose of `twitterImg` only if you think it will draw people to read your post.

How do you know what it will look like?
You can check the Twitter metadata by pasting a post's preview link in the [Twitter card validator](https://cards-dev.twitter.com/validator). 
You might have to click the validator twice.


