# (APPENDIX) Appendix {-}

# Post template in Markdown {#templatemd}

Use of this template is described in [Start the post from a template](#templates) and [Walkthrough with code snippets](#usetemplates).

Markdown template to be saved as `/content/blog/YYYY-MM-DD-slug/index.md`

You can hover over the top-right corner of the template to make a copy-paste button appear.

```{r posttemplatemd, results="asis"}
show_template("post-template.md", lang = "markdown")
```

# Post template in R Markdown {#templatermd}

Use of this template is described in [Start the post from a template](#templates) and [Walkthrough with code snippets](#usetemplates).

R Markdown template to be saved as `/content/blog/YYYY-MM-DD-slug/index.Rmd`

[Available on GitHub](https://github.com/ropensci-org/blog-guidance/blob/master/templates/post-template.Rmd) (_not displayed for copy-paste because of "html_preserve" tags_)

# Author file template {#authortemplate}

Use of this template is described in [Create or update your author file](#createauthorfile).

Author file template to be saved as `/content/authors/yourfirstname-yourlastname/_index.md` as described in [Technical Guidelines](#createauthorfile).

You can hover over the top-right corner of the template to make a copy-paste button appear.

```{r authorfiletemplate, results="asis"}
show_template("author-file-template.md", lang = "yaml")
```

# Author checklist for a post about a peer-reviewed package {#authorchecklistpeer}

Use of this template is described in [Pre-submission checks](#presubchecks).

Copy this checklist into the first comment on your pull request.
You can hover over the top-right corner of the template to make a copy-paste button appear.

```{r checklistpkg2, echo = FALSE}
show_checklist(c("submission-checklist.csv", "submission-checklist-peer-reviewed-pkg.csv"))
```

# Author checklist for any other post {#authorchecklistany}

Use of this template is described in [Pre-submission checks](#presubchecks).

Copy this checklist into the first comment on your pull request. 
You can hover over the top-right corner of the template to make a copy-paste button appear.

```{r checklistother2, echo = FALSE}
show_checklist("submission-checklist.csv")
```

# Editor checklist for a post about a peer-reviewed package {#editorchecklistpeer}

Use of this template is described in [Review a Post](#review).

Copy this checklist to your GitHub review summary.
You can hover over the top-right corner of the template to make a copy-paste button appear.

```{r checklisteditor2, echo = FALSE}
show_checklist(c("editor-checklist.csv", "editor-checklist-peer-reviewed-pkg.csv"))
```

# Editor checklist for any other post {#editorchecklistany}

Use of this template is described in [Review a Post](#review).

Copy this checklist to your GitHub review summary.
You can hover over the top-right corner of the template to make a copy-paste button appear.

```{r checklisteditorprp2, echo = FALSE}
show_checklist("editor-checklist.csv")
```
