# (APPENDIX) Appendix {-}

# Post template in Markdown {#templatemd}

INSTRUCT author to copy this template, or get it from roblog

```{r posttemplate, results="asis"}
show_template("post-template.md", lang = "markdown")
```

# Post template in R Markdown {#templatermd}

[R Markdown template](https://github.com/rosadmin/blog-guidance/blob/master/templates/author-file-template.Rmd) to be saved as `/content/blog/YYYY-MM-DD-slug/index.md`

# Author checklist for a post about a peer-reviewed package

```{r checklistpkg2, echo = FALSE}
show_checklist(c("submission-checklist.csv", "submission-checklist-peer-reviewed-pkg.csv"))
```

# Author checklist for any other post

```{r checklistother2, echo = FALSE}
show_checklist("submission-checklist.csv")
```

# Author file template {#authortemplate}

INSTRUCT author to copy this template, or get it from roblog

```{r authorfiletemplate, results="asis"}
show_template("author-file-template.md", lang = "yaml")
```

# Editor checklist for a post about a peer-reviewed package

```{r checklisteditor2, echo = FALSE}
show_checklist(c("editor-checklist-peer-reviewed-pkg.csv", "editor-checklist.csv"))
```

# Editor checklist for a post about any other peer-reviewed package

```{r checklisteditorprp2, echo = FALSE}
show_checklist("editor-checklist.csv")
```
