# (APPENDIX) Appendix {-}

# Post template in Markdown {#postmd}

INSTRUCT author to copy this template, or get it from roblog

```
```{r eval = !knitr::is_latex_output(), child="templates/post-template.md"}
```
```
```{r eval = knitr::is_latex_output(), child="templates/post-template.md"}
```


# Post template in R Markdown {#postrmd}

Maëlle please CREATE AND ADD Rmd template based on templates/post-template.md
INSTRUCT author to copy this template, or get it from roblog


# Author file template {#authortemplate}

INSTRUCT author to copy this template, or get it from roblog

ERROR when calling templates/author-file-template.md using ~same code as above: 
```
List of 2
 $ eval : language !knitr::is_latex_output()
 $ child: chr "templates/author-file-template.md"



processing file: ./templates/author-file-template.md
Quitting from lines 27-27 (./templates/author-file-template.md) 
Error in blks | head(c(TRUE, txts), -1) : 
  operations are possible only for numeric, logical or complex types
Calls: local ... lapply -> FUN -> knit -> process_file -> split_file

Execution halted
<simpleError in Rscript_render(f, render_args, render_meta): Failed to compile appendix.Rmd>
```


