#  (PART) Editor Guide {-}

# Review, Publish, Promote {#editor}

## Review a Post
This section explains how to review a blog post or tech note.
The editor for a post is typically the Community Manager or their intern.

A post is submitted as a pull request on GitHub and we use the [well documented GitHub web interface](https://help.github.com/en/github/collaborating-with-issues-and-pull-requests/reviewing-proposed-changes-in-a-pull-request) to suggest edits, make comments, and ultimately merge the pull request to publish the post.

### Review

ADD screenshot(s) of review interface

Read the post preview to get "a feel" for it. On my first read, I (Stefanie) typically make a few notes for myself (pen & paper) on what to pay attention to on deeper review.
This is when I often note some positive feedback, based on a first impression.

Click on the 'Files changed' tab in the pull request to view the .Rmd or .md file for the post.

Copy and paste either the Editor checklist for a post about a peer-reviewed package, or the Editor checklist for any other post, into the window that appears when you click the green "Review changes" button.

Carry out those checks and comment as needed inline in the .Rmd or .md file.

When adding your first comment, choose 'Start a revew' (not 'Add a single comment'), so the author gets a single notification for the review when it is complete.

Where changes are "obvious" such as fixing grammar or a typo, use GitHub "commit suggestion" `<cmd-g>` so the author can commit your change directly. 
Comment to explain the change if needed, for instance if the diff displayed by GitHub does not highlight what word(s) where edited.

To ask the author to address a comment, provide a link to the appropriate section of this book to guide them.

After all inline commenting is done, copy the editor response text sample to the Review window and add any further notes, including your overall impression.
Tell the author if you have updated their author metadata (author file) e.g. by fixing the folder name, or adding a Twitter handle.
There is always something great in a post to highlight in your review. 
Be specfic.
If the post or something in it excites you, don't hesitate to say that.
How else will the author know and be inspired?!

Sample editor response text is not written yet but here are some things to include:

- I have made <n> comments. Look for 'hidden comments' when there are more than x comments.
- ask for thumbs up or thumbs down on every editor comment so we know you have seen it
- 'Resolve conversation' for items you have addressed
- It's ok to disagree with some comments
- tag Editor when you have finished addressing their comments

When your review is complete, click 'Comment' or 'Request changes', at your discretion. 
This will trigger a notificaton to the author

To download a PR locally so that you can experiment with it, run [`usethis::pr_fetch(<pr_number>)`](https://usethis.r-lib.org/reference/pr_init.html)
Even if an author gives edit permission to the repo maintainer, the Editor does not usually make edits directly on the post.
There are exceptions.

### Checklist for a post about a peer-reviewed package

```{r checklisteditorprp, echo = FALSE}
show_checklist(c("editor-checklist-peer-reviewed-pkg.csv", "editor-checklist.csv"))
```

### Checklist for any other post

```{r checklisteditor, echo = FALSE}
show_checklist("editor-checklist.csv")
```

### Note about non automatic tech checks

The roblog helpers do not check

* whether the alternative text of an image is informative,
* whether a title is in Title Case.

While we recommend that authors add [line breaks at the end of every sentence, after the period](https://cirosantilli.com/markdown-style-guide#line-wrapping), we do not ask them to add these in their draft after the fact.


### Check Twitter metadata

The Twitter metadata in a post's YAML helps it "look good" when an account like R Weekly Live or other readers link to the post in a tweet, separate from [the tweet _we_ send](#tweetpromo). 
Therefore it is important to check the Twitter metadata by pasting a post's preview link in the [Twitter card validator](https://cards-dev.twitter.com/validator).

The relevant YAML tags are `twitterImg`, `description`, `title`.
These same metadata tags might be picked up by other platforms such as Slack).

## Publish a Post
Publish a post by merging its pull request.
For a post dated e.g. 2020-02-28, you can merge it any time after ~5pm Pacific on 2020-02-27 i.e. when it's Feb 28th somewhere in the world.
When possible, it's nice to have a post published by morning in the timezone of the main post author. 

Editor adds the YAML `topicid` of a post by adding an entry - called a "topic" for the post in our [discussion forum blogs category](https://discuss.ropensci.org/c/blog/).
When an entry is created, the topicid is the number at the end of the topic's URL. 
E.g. for [this topic](https://discuss.ropensci.org/t/we-cleaned-our-website-urls-with-r/1904), `https://discuss.ropensci.org/t/we-cleaned-our-website-urls-with-r/1904`, the `topicid` is `1904`.

## Promote a Post on Twitter {#tweetpromo}

### Workflow

Tweet from [rOpenSci](https://twitter.com/rOpenSci).

We tweet at ~8am Pacific, but it would be good to use a system for optimizing the time to send a tweet (e.g. using Buffer). 

Note that in Tweetdeck you can schedule an individual tweet, but you cannot schedule subsequent tweets in a thread.
Therefore, it's best to draft tweets in advance (e.g. while reviewing the post) and have a feature image(s) and alternative text for the image ready to use.
Stef uses a private google doc called "scratchpad" for this, and saves images in a local folder. 

### Content

The first tweet of a thread or only tweet _must_ include

* the post title,
* a link to the post,
* tag the author's account, or their IRL name,

Any tweet _must_ provide an alternative description of any included image.

A further tweet _can_ include a link to the software peer review thread.

Any tweet _can_ include

* hashtags,
* additional account names,

with the caveats of the next subsections.

### Tagging accounts

Tag the account(s) of all post authors and package authors and reviewers. 

If not already included in their author metadata, you can search for their account but only tag them if

* it is active,
* it is not anonymous,
* it is at least partly used professionally by the owner.

When in doubt, use the person's name, or time-permitting, contact the person whose account you'd like to tag.

For a package wrapping a service present on Twitter you can tag that account (e.g. for a tweet about `rredlist` that accesses IUCN Red List you might tag IUCN Twitter account).

When tagging accounts include them in a sentence e.g. "Thanks to `@account1`"/ "As told by `@account2`". 
We do not use tagging in tweets to ask for attention (i.e. no account names used liked hashtags at the bottom of a tweet).

### Using hashtags

#### Selecting relevant hashtags

For a tweet about a post related to a package or any R thing, use the `#rstats` hashtag.

For a tweet about a package post, make the package name a hashtag, since [rocitations Twitter account](https://twitter.com/rocitations) does this to announce package citations.

Check the last tweets using any hashtag except the `#rstats` hashtag to see whether it is used as you think it would.
E.g. using `httr` wouldn't be a good idea. It is a package name but on Twitter it is the hashtag of [a team with a name controversy](https://en.wikipedia.org/wiki/Washington_Redskins_name_controversy) and even has its own emoji automatically attached to it by Twitter. 

#### Adding hashtags

Do not use too many hashtags in any tweet so as not to make the account look like a spam account / greedy for attention.

Post hashtags at the bottom of each tweet, to make the rest of the content of the tweet easier to read.

[Capitalize letters of each word](https://www.boia.org/blog/make-your-hashtags-accessible) for hashtags including several words i.e. use lower or upper camelCase (e.g. `#RLadies` not `#rladies`). 

When posting a thread, use each hashtag only once so as not to pollute the timeline of that hashtag.

### Using emojis 

In tweets, emojis are optional. 
When using emojis, [do not use too many of them](https://www.a11ywithlindsey.com/blog/7-ways-tweets-more-accessible).

### Using gifs

In tweets, gifs are optional.

* One can include a gif that was created for the post (e.g. an animated plot)
* But generally not a Giphy gif since it might be interpreted differently by people who know more/less context about the gif in question (e.g. a TV show)
* When using a gif we should [add their description](https://www.a11ywithlindsey.com/blog/7-ways-tweets-more-accessible) by typing [Gif alt: descriptive phrase] at the bottom of the tweet 
* When tweeting from twitter.com, as of Feb 2020, if you have the "compose image descriptions" setting turned on in your accessibility settings, you can add alt descriptions for gifs as you do for images

### Example 2-tweet thread:

```
[blog] “rmangal: making ecological networks easily accessible” 

New post by @KCazelles & @SVissault in our Software Peer Review series 

🔗 https://ropensci.org/blog/2019/10/21/rmangal/

1/2 
#rstats #rmangal #SoftwarePeerReview
```

```
Shoutouts 🙏 in the post to reviewers Anna Willoughby & @thomasp85, rmangal contributors https://docs.ropensci.org/rmangal/authors.html, & all ecologists who have spent countless hours collecting data

🔎Read the rmangal open software peer review thread: https://github.com/ropensci/software-review/issues/332

2/2 

```
