#  (PART) Editor Guide {-}

# Review, Publish, Promote {#editor}

```{block, type='summaryblock', echo=TRUE}
This chapter outlines the workflow for an editor to review, publish and promote a blog post or tech note. It may also provide insights for post authors.
```

## Review a post {#review}
This section explains how to review a blog post or tech note.
The editor for a post is typically the Community Manager or their intern.

A post is submitted as a pull request on GitHub. 
We use the [well documented GitHub web interface](https://help.github.com/en/github/collaborating-with-issues-and-pull-requests/reviewing-changes-in-pull-requests) to suggest edits, make comments, and ultimately merge the pull request to publish the post.
There's no better resource than that for screenshots and guidance on reviewing pull requests and for links to share with an author when coaching them on how to respond to your review. 

These are particularly helpful:

- [About pull request reviews](https://help.github.com/en/github/collaborating-with-issues-and-pull-requests/about-pull-request-reviews)
- [Reviewing proposed changes in a pull request](https://help.github.com/en/github/collaborating-with-issues-and-pull-requests/reviewing-proposed-changes-in-a-pull-request)
- [Incorporating feedback in your pull request](https://help.github.com/en/github/collaborating-with-issues-and-pull-requests/incorporating-feedback-in-your-pull-request)

### Review

Read the post preview to get a feel for it. On my first read, I (Stefanie) typically make a few pen & paper notes for myself on what to pay attention to on deeper review.
This is when I often note some positive feedback, based on a first impression.
There is always something great in a post to highlight in your review. 
Be specific.
If the post or something in it excites you, don't hesitate to say that.
How else will the author know and be inspired?!

To start your review of the pull request, copy and paste either the [editor checklist for a post about a peer-reviewed package](#editorchecklistpeer), or the [editor checklist for any other post](#editorchecklistany), into the box that appears when you click the green _Review changes_ button.

Click on the _Files changed_ tab in the pull request to view the .Rmd or .md file for the post.
Complete the checklist and comment as needed inline in the .Rmd or .md file.
You must comment in the .Rmd if one was submitted.

When adding your first comment, choose _Start a review_ (not _Add a single comment_), so the author gets a single notification for the review when it is complete.

Where changes are "obvious" such as fixing grammar or a typo, use GitHub ["commit suggestion" `<cmd-g>`/`<ctrl-g>`](https://help.github.com/en/github/collaborating-with-issues-and-pull-requests/commenting-on-a-pull-request#adding-line-comments-to-a-pull-request) so the author can commit your change directly. 
Comment to explain the change if needed, for instance if the diff displayed by GitHub does not highlight which word(s) were edited.

While our [Style Guide](#styleguide) recommends that authors add [line breaks at the end of every sentence](https://cirosantilli.com/markdown-style-guide#line-wrapping), we do not ask them to add these in their draft after the fact.

To download a pull request locally so that you can experiment with it, run [`usethis::pr_fetch(<pr_number>)`](https://usethis.r-lib.org/reference/pr_init.html).
Even if an author gives edit permission to the repo maintainer, the editor does not usually make edits directly on the post.
Rare exceptions can be made at the editor's discretion.

To ask the author to address a comment, provide a link to the appropriate section of this book to guide them.

After all inline commenting and the checklist is done, add any further notes, starting with a positive comment and your overall impression, to the _Review changes_ box.
Tell the author if you have updated their author metadata (author file) e.g. by fixing the folder name, or adding a Twitter handle.
This helps draw their attention to this nice feature.

We don't (yet?) have templated editor response text, but here are helpful things to include:

- I have made ~n (number of) comments. Look for _hidden conversations_ when there are many comments.
- Ask for thumbs up or thumbs down on every editor comment so we know you have seen it.
- It's ok to disagree with some comments.
- [_Resolve conversation_](https://help.github.com/en/github/collaborating-with-issues-and-pull-requests/commenting-on-a-pull-request#resolving-conversations) for items you have addressed.
- Tag editor when you have finished addressing their comments.

When your review is complete, click [_Comment_, _Approve_, or _Request changes_](https://help.github.com/en/github/collaborating-with-issues-and-pull-requests/reviewing-proposed-changes-in-a-pull-request#submitting-your-review), at your discretion. 
This will trigger a notificaton to the author.

### Editor checklist - Posts on peer-reviewed packages

```{r checklisteditorprp, echo = FALSE}
show_checklist(c("editor-checklist.csv", "editor-checklist-peer-reviewed-pkg.csv"))
```

### Editor checklist - Other posts

```{r checklisteditor, echo = FALSE}
show_checklist("editor-checklist.csv")
```

### Check Twitter metadata

The Twitter metadata in a post's YAML helps it "look good" when an account like R Weekly Live or other readers link to the post in a tweet, separate from [the tweet _we_ send](#tweetpromo). 
Therefore it is important to check the Twitter metadata by pasting a post's preview link in the [Twitter card validator](https://cards-dev.twitter.com/validator).
You might have to click twice.

See [Understanding Twitter cards](#twittercards) for details. 
Perfecting metadata for Twitter cards is optional for authors, so decide how critical any changes are before requesting them in your review.

## Publish a post {#publish}
Publish a post by merging its pull request.
For a post dated e.g. 2020-02-28, you can merge it any time after ~5pm Pacific on 2020-02-27 i.e. when it's Feb 28th somewhere in the world.
When possible, it's nice to have a post published by morning in the timezone of the main post author. 

A "topic" linked to the blog post will automatically be created in the [discussion forum blogs category](https://discuss.ropensci.org/c/blog/) for both blog posts and tech notes. This facilitates commenting on posts. Comments will appear both below the post and in the discussion forum.

_Note about older posts:_ Very old posts from (before March 2017) have no comments at all; these posts have no `topicid` field in their YAML header. Newer posts (March 2017 onward) have a yaml field `topicid` and a number in it that links to a topic that we manually created in the forum. Posts newer than March 9, 2020 won't have a `topicid` field in their YAML header as a forum topic is automatically created.

## Promote a post on Twitter {#tweetpromo}

### Workflow

Tweet from [rOpenSci](https://twitter.com/rOpenSci).

We tweet at ~8am Pacific, but it would be good to use a system for optimizing the time to send a tweet (e.g. using Buffer). 

Note that in Tweetdeck you can schedule an individual tweet, but you cannot schedule subsequent tweets in a thread.
Therefore, it's best to draft tweets in advance (e.g. while reviewing the post) and have a feature image(s) and alternative text for the image ready to use.
Stef uses a private Google doc called "scratchpad" for this, and saves images in a local folder. 

### Content

The first tweet of a thread or only tweet _must_ include

* the post title,
* a link to the post,
* tag the author's account, or their IRL name,

Any tweet _must_ provide an alternative description of any included image.

A further tweet _can_ include a link to the software peer review thread.

Any tweet _can_ include

* hashtags,
* additional account names,

with the caveats of the next subsections.

### Tagging accounts

Tag the account(s) of all post authors and package authors and reviewers. 

If not already included in their author metadata, you can search for their account but only tag them if

* it is active,
* it is not anonymous,
* it is at least partly used professionally by the owner.

When in doubt, use the person's name, or time permitting, contact the person whose account you'd like to tag.

For a package wrapping a service present on Twitter you can tag that account (e.g. for a tweet about `rredlist` that accesses IUCN Red List you might tag IUCN Twitter account).

When tagging accounts include them in a sentence e.g. "Thanks to `@account1`"/ "As told by `@account2`". 
We do not use tagging in tweets to ask for attention (i.e. no account names used like hashtags at the bottom of a tweet) because it could be viewed as spamming mentioned accounts, and because it creates visual clutter in the tweet.

### Using hashtags

#### Selecting relevant hashtags

For a tweet about a post related to a package or any R thing, use the `#rstats` hashtag.

For a tweet about a package post, make the package name a hashtag, since [rocitations Twitter account](https://twitter.com/rocitations) does this to announce package citations.

Check the last tweets using any hashtag except the `#rstats` hashtag to see whether it is used as you expect.
E.g. using `httr` wouldn't be a good idea. It is a package name but on Twitter it is the hashtag of [a team with a name controversy](https://en.wikipedia.org/wiki/Washington_Redskins_name_controversy) and even has its own emoji automatically attached to it by Twitter. 

#### Adding hashtags

Do not use too many hashtags in any tweet so as not to make the account look like a spam account / greedy for attention.

Post hashtags at the bottom of each tweet, to make the rest of the content of the tweet easier to read.

[Capitalize letters of each word](https://www.boia.org/blog/make-your-hashtags-accessible) for hashtags including several words i.e. use lower or upper camelCase (e.g. `#RLadies` not `#rladies`). 

When posting a thread, use each hashtag only once so as not to pollute the timeline of that hashtag.

### Using emojis 

In tweets, emojis are optional. 
When using emojis, [do not use too many of them](https://www.a11ywithlindsey.com/blog/7-ways-tweets-more-accessible).

### Using gifs

In tweets, gifs are optional.

* One can include a gif that was created for the post (e.g. an animated plot).
* But generally not a Giphy gif since it might be interpreted differently by people who know more/less context about the gif in question (e.g. a TV show).
* When using a gif we should [add its description](https://www.a11ywithlindsey.com/blog/7-ways-tweets-more-accessible) by typing `[Gif alt: descriptive phrase]` at the bottom of the tweet.
* When tweeting from twitter.com, as of Feb 2020, if you have the _compose image descriptions_ setting turned on in your accessibility settings, you can add alt descriptions for gifs as you do for images.

### Example 2-tweet thread:

```
[blog] “rmangal: making ecological networks easily accessible” 

New post by @KCazelles & @SVissault in our Software Peer Review series 

🔗 https://ropensci.org/blog/2019/10/21/rmangal/

1/2 
#rstats #rmangal #SoftwarePeerReview
```

```
Shoutouts 🙏 in the post to reviewers Anna Willoughby & @thomasp85, rmangal contributors https://docs.ropensci.org/rmangal/authors.html, & all ecologists who have spent countless hours collecting data

🔎Read the rmangal open software peer review thread: https://github.com/ropensci/software-review/issues/332

2/2 

```
