#  (PART) Editor Guide {-}

# Review, Publish, Promote {#editor}

## Review a Post
This section explains how to review a post.
The editor for a post is typically the Community Manager or their intern.

A post is submitted as a pull request on GitHub and we use the [well documented GitHub web interface](https://help.github.com/en/github/collaborating-with-issues-and-pull-requests/reviewing-proposed-changes-in-a-pull-request) to suggest edits, make comments, and ultimately merge the pull request to publish the post.

To ask the author to address a comment, provide a link to the appropriate section of this book to guide them.

Copy and past one of the checklists below depending on the type of posts you are reviewing (about a peer-reviewed package or not).

### Checklist for a post about a peer-reviewed package

```{r checklisteditorprp, echo = FALSE}
show_checklist(c("editor-checklist-peer-reviewed-pkg.csv", "editor-checklist.csv"))
```

### Checklist for any other post

```{r checklisteditor, echo = FALSE}
show_checklist("editor-checklist.csv")
```

### Note about non automatic tech checks

The roblog helpers do not check

* whether the alternative text of an image is informative,
* whether a title is in Title Case.

Furthermore, do not ask for an author to add line returns after they wrote their post.
We prefer authors to add such line breaks but should not make them correct their draft after the fact.

### Note about Twitter metadata

A further section concerns [the tweet _we_ send](#tweetpromo) about a post but the post will be shared by other accounts (R Weekly Live, some readers).
Therefore it is important to check Twitter metadata of a post by pasting its preview link in [Twitter card validator](https://cards-dev.twitter.com/validator).
Relevant YAML tags are `twitterImg`, `description`, `title`.
Furthermore, the same metadata tags might be picked up by other platforms (e.g. Slack).

## Publish a Post
Publish a post by merging its pull request.
For a post dated e.g. 2020-02-28, you can merge it any time after ~5pm Pacific on 2020-02-27 i.e. when it's Feb 28th somewhere in the world.
When possible, it's nice to have a post published by morning in the timezone of the main post author. 

Editor adds the YAML `topicid` of a post by adding an entry - called a "topic" for the post in our [discussion forum blogs category](https://discuss.ropensci.org/c/blog/).
When an entry is created, the topicid is the number at the end of the topic's URL. 
E.g. for [this topic about a tech note](https://discuss.ropensci.org/t/we-cleaned-our-website-urls-with-r/1904), `https://discuss.ropensci.org/t/we-cleaned-our-website-urls-with-r/1904`, the `topicid` is `1904`.

## Promote a Post on Twitter {#tweetpromo}

### Workflow

Tweet from [rOpenSci](https://twitter.com/rOpenSci).

We tweet at ~8am Pacific, but it would be good to use a system for optimizing the time to send a tweet (e.g. using Buffer). 

Note that in Tweetdeck you can schedule an individual tweet, but you cannot schedule subsequent tweets in a thread.
Therefore, it's best to draft tweets in advance (e.g. while reviewing the post) and have a feature image(s) and alternative text for the image ready to use.

### Content

The first tweet of a thread or only tweet _must_ include

* the post title,
* a link to the post,

Any tweet _must_ provide an alternative description of any included image.

A further tweet _can_ include a link to the software peer review thread.

Any tweet _can_ include

* hashtags,
* account names,

with the caveats of the next subsections.

### Tagging accounts

Only tag the account of an author if they included their username in their author file.
For reviewers, you might search the account but only tag an account

* it is active,
* it is not anonymous,
* it is at least partly used professionally by the owner.
In case of doubt contact the person whose account you'd like to tag.

For a package wrapping a service present on Twitter (e.g. for a tweet about `rredlist` that accesses IUCN Red List you would tag IUCN Twitter account).

### Using hashtags

#### Selecting relevant hashtags

For a tweet about a post related to a package or any R thing, use the `#rstats` hashtag.
For a tweet about a package post, make the package name a hashtag, since [rocitations Twitter account](https://twitter.com/rocitations) does this to announce package citations.

#### Adding hashtags

Do not use too many hashtags in any tweet so as not to make the account look like a spam account / greedy for attention.

Post hashtags at the bottom of each tweet, to make the rest of the content of the tweet easier to read.

[Capitalize letters of each word](https://www.boia.org/blog/make-your-hashtags-accessible) for hashtags including several words i.e. use lower or upper camelCase (e.g. `#RLadies` not `#rladies`). 

When posting a thread, use each hashtag only once so as not to pollute the timeline of that hashtag.

### Emoji use

In tweets, emojis are optional. 
When using emojis, [do not use too many of them](https://www.a11ywithlindsey.com/blog/7-ways-tweets-more-accessible).

### Example 2-tweet thread:

```
[blog] “#rmangal: making ecological networks easily accessible” 

New post by @KCazelles & @SVissault in our #SoftwarePeerReview series 

🔗 https://ropensci.org/blog/2019/10/21/rmangal/

1/2 
#rstats
```

```
Shoutouts 🙏 in the post to reviewers Anna Willoughby & @thomasp85, rmangal contributors https://docs.ropensci.org/rmangal/authors.html, & all ecologists who have spent countless hours collecting data

🔎Read the #rmangal open #softwarepeerreview thread: https://github.com/ropensci/software-review/issues/332

2/2 
#rstats
```

sample messages for authors and reviewers as in [JOSS docs](https://joss.readthedocs.io/en/latest/editing.html#sample-messages-for-authors-and-reviewers)